ms2

### 2017-09-26 ms1/ms1_display.Rmd
small cleanups

```{r approp_graph}
pde_approp_table = read_tsv('tables/pde_approp_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  (function(df) bind_rows(
    df,
    df %>% group_by(year, tier) %>%
      summarize(n=sum(n)) %>%
      mutate(antibiotic='overall')
  )) %>%
  filter(antibiotic %in% c(top_abx, 'overall')) %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

pde_approp_table %>%
  ggplot(aes(x=factor(year), y=f, fill=factor(tier))) +
  geom_bar(stat='identity') +
  facet_grid(~antibiotic) +
  theme_classic()
```

@@

If a drug declined by $X$, then the optimal change in the high tier fraction would be $1/(1-X) \approx 1+X$. For example, overall prescribing fell by about 5%, and high-tier prescribing increased by 2.5%. Azithromycin prescribing fell by about 20%, and high-tier azithro prescribing rose by only 6%.

>>>>

```{r approp_graph}
pde_approp_table = read_tsv('tables/pde_approp_table.tsv') %>%
  #filter(year %in% c(2011, 2014)) %>%
  (function(df) bind_rows(
    df,
    df %>% group_by(year, tier, refill) %>%
      summarize(n=sum(n)) %>%
      mutate(antibiotic='overall')
  )) %>%
  filter(antibiotic %in% c(top_abx, 'overall')) %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

pde_approp_table %>%
  filter(year %in% c(2011, 2014)) %>%
  ggplot(aes(x=factor(year), y=f, fill=factor(tier))) +
  geom_bar(stat='identity') +
  facet_grid(~antibiotic) +
  theme_classic()
```

@@

If a drug declined by $X$, then the optimal change in the high tier fraction would be $1/(1-X) = 1+X + \mathcal{O}(X^2)$. For example, overall prescribing fell by about 5%, and high-tier prescribing increased by 2.5%. Azithromycin prescribing fell by about 20%, and high-tier azithro prescribing rose by only 6%.

### 2017-09-26 ms2/ms2_display.Rmd
small cleanups

```{r fnz_mu_results}
results %>%
  filter(unit_type=='hrr', model %in% c('univariate_fnz', 'multivariate_fnz_mean', 'multivariate_fnz_mup'), term != '(Intercept)') %>%
  (function(df) {
    filter(df, term != 'fnz', p.adjust(p.value, method='BH') < 0.05) %>%
      select(bug, drug_group) %>%
      distinct() %>%
      inner_join(df, by=c('bug', 'drug_group')) }) %>%
  mutate(model=str_replace(model, '^multivariate_', '')) %>%
  select(bug, drug_group, model, term, estimate) %>%
  spread(term, estimate) %>%
  kable
```

>>>>

```{r fnz_mu_results}
results %>%
  filter(unit_type=='hrr', model %in% c('univariate_fnz', 'univariate_mup', 'multivariate_fnz_mean', 'multivariate_fnz_mup'), term != '(Intercept)') %>%
  (function(df) {
    filter(df, term != 'fnz', p.adjust(p.value, method='BH') < 0.05) %>%
      select(bug, drug_group) %>%
      distinct() %>%
      inner_join(df, by=c('bug', 'drug_group')) }) %>%
  mutate(model=str_replace(model, '^multivariate_', '')) %>%
  select(bug, drug_group, model, term, estimate) %>%
  spread(term, estimate) %>%
  kable
```
